### 2014-10-21 paper/include/dtail.tex
dtail
git write write pull

When a row is to be scheduled for refresh the refresh data is checked. If the row is valid and the time since the last refresh is \(64\:ms \times 2^n, n = [0..7]\) a refresh is performed, otherwise not. The refreshes can be done either by ROR or by CBR depending on what is most efficient at the time. If a large number of rows need refresh then CBR is selected, otherwise ROR is used.

@@

>>>>

When a row is selected for refresh by the memory controller, DTail intercepts the refresh command and based on the Retention Time and Validity information either lets the refresh to be performed or cancels it. The method used for refreshing a row depends on what is the most efficient at the time, if a large number of rows need refresh then CBR is selected, otherwise ROR is used.

@@

Comparing DTail with the somewhat similar RAIDR, Cui et al. achieves a bigger decrease in refresh operations compared to what Liu et al. does. This is due to DTail-R having a higher granularity as the refresh rate is kept per row and not per row group as in RAIDR.
